Reproducibility and plant pathology: where do we stand and a way forward

### 2021-06-16 analysis/paper/paper.Rmd
Update affiliations, use word_document2, move libs to frontmatter

---
title: "Reproducibility and plant pathology: where do we stand and a way forward"
author:
  - Adam H. Sparks:
      email: Adam.Sparks@dpird.wa.gov.au
      institute: DPIRD, USQ
      correspondence: true
  - Emerson Del Ponte:
      institute: UFV
  - Kaique dos Santos Alves:
      institute: UFV
  - Zachary Foster:
      institute: OSU
  - Niklaus J. Grünwald:
      institute: ARS
institute:
  - DPIRD: Department of Primary Industries and Regional Development, Farming Systems Innovation, Perth WA 6000, Australia
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis, OR, USA
  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis, OR, USA
output: 
# Uncomment from line 25 to 45 and comment 46 to line 54 for Word output
# Comment from line 25 to 45 and uncomment 46 to line 54 for LaTeX output
#  officedown::rdocx_document:
#      fig_caption: yes
#      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
#      pandoc_args:
#        - '--lua-filter=scholarly-metadata.lua'
#        - '--lua-filter=author-info-blocks.lua'
#        - '--lua-filter=pagebreak.lua'
#      tables:
#        layout: autofit
#        width: 1.0
#        caption:
#          style: Table Caption
#          pre: 'Table '
#          sep: ': '
#        conditional:
#          first_row: true
#          first_column: false
#          last_row: false
#          last_column: false
#          no_hband: false
#          no_vband: true
    pdf_document:
        keep_tex: true
        latex_engine: xelatex
        pandoc_args:
          - '--lua-filter=scholarly-metadata.lua'
          - '--lua-filter=author-info-blocks.lua'
          - '--lua-filter=pagebreak.lua'
documentclass: article
classoption: letterpaper
fontsize: 12pt
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage[T1]{fontenc}
   - \usepackage{helvet}
   - \renewcommand{\familydefault}{\sfdefault}
bibliography: references.bib
csl: "../templates/american-phytopathological-society.csl" # Insert path for the bib-style
keywords: |
  open science; open data; reproducible research; FAIR data
highlights: |
  Open research practices are highlighted extensively in the broader scientific community. Our survey of 300 randomly selected articles from 2012 to 2018 indicates that we have work to do in this area as plant pathologists with most articles scoring low in openness and reproducibility.
---

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.path = "../figures/",
  dev = c("postscript"),
  fig.width = 3.31,
  fig.height = 3.31,
  out.width = "100%",
  dpi = 300,
  comment = "#>",
  dev = "cairo_pdf"
)

library("Reproducibility.in.Plant.Pathology")
```

@@

# Abstract

@@

# Introdution

>>>>

---
title: "Reproducibility and plant pathology: where do we stand and a way forward"
author:
  - Adam H. Sparks:
      email: Adam.Sparks@dpird.wa.gov.au
      institute: DPIRD, USQ
      correspondence: true
  - Emerson Del Ponte:
      institute: UFV
  - Kaique dos Santos Alves:
      institute: UFV
  - Zachary Foster:
      institute: OSU
  - Niklaus J. Grünwald:
      institute: ARS
institute:
  - DPIRD: Department of Primary Industries and Regional Development, Farming Systems Innovation, Perth WA 6000, Australia
  - USQ: University of Southern Queensland, Centre for Crop Health, Toowoomba Qld 4350, Australia
  - UFV: Departmento de Fitopatologia, Universidade Federal de Viçosa, Brazil
  - OSU: Department of Botany and Plant Pathology, Oregon State University, Corvallis OR 97331, USA
  - ARS: Horticultural Crops Research Unit, USDA Agricultural Research Service, Corvallis OR 97331, USA
output: 
  bookdown::word_document2:
     fig_caption: yes
     number_sections: FALSE
     reference_docx: "../templates/template.docx" # Insert path for the DOCX file
     pandoc_args:
       - '--lua-filter=scholarly-metadata.lua'
       - '--lua-filter=author-info-blocks.lua'
       - '--lua-filter=pagebreak.lua'
classoption: letterpaper
fontsize: 12pt
bibliography: references.bib
link-citations: no
csl: "../templates/american-phytopathological-society.csl" # Insert path for the bib-style
---

```{r, setup, echo = FALSE, message=FALSE}
library("officer")
library("dplyr")
library("janitor")
library("flextable")
library("Reproducibility.in.Plant.Pathology")
library("tidyr")
library("DiagrammeR")
library("DiagrammeRsvg")
library("rsvg")
library("ggplot2")
library("patchwork")

knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.path = "../figures/",
  dev = c("postscript"),
  fig.width = 3.31,
  fig.height = 3.31,
  out.width = "100%",
  dpi = 300,
  comment = "#>",
  dev = "cairo_pdf",
  cache = TRUE
)
```

**Keywords: open science, open data, reproducible research, FAIR data**

@@

# Abstract {-#abstract}

@@

# Introduction
